Bayesian regression facilitates quantitative modelling of cell metabolism

### 2023-10-31 paper/main.qmd
keywords

---
title: "Bayesian regression facilitates quantitative modelling of cell metabolism"
keywords: Bayesian inference, kinetic models of cell metabolism 
abstract: >
  This paper presents Maud, a command-line application that implements Bayesian
  statistical inference for kinetic models of biochemical metabolic reaction
  networks. Maud takes into account quantitative information from omics
  experiments and background knowledge, as well as structural information about
  kinetic mechanisms, regulatory interactions and enzyme knockouts. Our paper
  reviews the existing options in this area, presents a case study illustrating
  how Maud can be used to analyse a metabolic network and explains the
  biological, statistical and computational design decisions underpinning Maud.
number-sections: true
author: 
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliations: 
      - id: biosustain
        name: DTU
        department: DTU Biosustain
        city: Kongens Lyngby
        country: Denmark
    attributes:
      corresponding: true
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Nicholas Luke Cowie"
    affiliations: 
      - id: biosustain
        name: DTU
        department: DTU Biosustain
        city: Kongens Lyngby
        country: Denmark
    attributes:
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Lars Keld Nielsen"
    affiliations: 
      - name: The University of Queensland
        department: Australian Institute for Bioengineering and Nanotechnology (AIBN)
        city: St Lucia
        country: Australia
      - id: biosustain
        name: DTU
        department: DTU Biosustain
        city: Kongens Lyngby
        country: Denmark
bibliography: bibliography.bib
format:
  acs-pdf:
    keep-tex: true
    journal:
      id: asbcd6  #This is an identifier for the target journal: from https://pubs.acs.org/, the identifier is the part of the URL after https://pubs.acs.org/journal/, e.g. for J. Org. Chem. it would be joceah.
      type: article  #article, note, communication, review, letter, or perspectivee
      layout: traditional #traditional or twocolumn, twocolumn currently broken for longtables
      hide-email: false # if enabled, hides email addresses (and fax/phone)
  acs-html:
   include-in-header: mathjax.html
   embed-resources: true
  docx: default
---

>>>>

---
title: "Bayesian regression facilitates quantitative modelling of cell metabolism"
keywords: Bayesian inference, kinetic models of cell metabolism, 
          multiomics integration, ordinary differential equations,
          regulatory anlaysis
abstract: >
  This paper presents Maud, a command-line application that implements Bayesian
  statistical inference for kinetic models of biochemical metabolic reaction
  networks. Maud takes into account quantitative information from omics
  experiments and background knowledge, as well as structural information about
  kinetic mechanisms, regulatory interactions and enzyme knockouts. Our paper
  reviews the existing options in this area, presents a case study illustrating
  how Maud can be used to analyse a metabolic network and explains the
  biological, statistical and computational design decisions underpinning Maud.
number-sections: true
author: 
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliations: 
      - id: biosustain
        name: DTU
        department: DTU Biosustain
        city: Kongens Lyngby
        country: Denmark
    attributes:
      corresponding: true
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Nicholas Luke Cowie"
    affiliations: 
      - id: biosustain
        name: DTU
        department: DTU Biosustain
        city: Kongens Lyngby
        country: Denmark
    attributes:
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Lars Keld Nielsen"
    affiliations: 
      - name: The University of Queensland
        department: Australian Institute for Bioengineering and Nanotechnology (AIBN)
        city: St Lucia
        country: Australia
      - id: biosustain
        name: DTU
        department: DTU Biosustain
        city: Kongens Lyngby
        country: Denmark
bibliography: bibliography.bib
format:
  acs-pdf:
    keep-tex: true
    journal:
      id: asbcd6  #This is an identifier for the target journal: from https://pubs.acs.org/, the identifier is the part of the URL after https://pubs.acs.org/journal/, e.g. for J. Org. Chem. it would be joceah.
      type: article  #article, note, communication, review, letter, or perspectivee
      layout: traditional #traditional or twocolumn, twocolumn currently broken for longtables
      hide-email: false # if enabled, hides email addresses (and fax/phone)
  acs-html:
   include-in-header: mathjax.html
   embed-resources: true
  docx: default
---
